%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\setlength{\columnsep}{1cm}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
 

\usepackage{tikz}

\usepackage{soul}

\graphicspath{ {./icons/} }

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Maximo}{Mugisha}{Senior Software Engineer}

\begin{multicols}{2}
\color{BlueGreen}
{\faHome} \quad
{\href{https://www.maximo.ug}{ www.maximo.ug}} \\

{\faMapMarker} \quad
{Kampala, Uganda} \\

{\faGithub} \quad
{\href{https://www.github.com/maximugisha}{maximugisha}} \\

{\faLinkedin} \quad
{\href{https://www.linkedin.com/in/maximugisha}{maximugisha}} \\

{\faEnvelope} \quad
{\href{mailto:maximugisha@gmail.com} {maximugisha@gmail.com}} \\

{\faWhatsapp} \quad
{\href{tel:+256702431725}{+256702431725}} \\

{\faPhone} \quad
{\href{tel:+256775097505}{+256775097505}} \\
\end{multicols}

\vspace{\topsep}

{Competent, forward-looking Computer and Software Engineer with 6+ years experience in creating and  innovating ideas into software solutions to enhance business productivity. Consistently recognized as a hands-on leader, skilled at project collaboration in cross-functional teams with a fast-paced, deadline-driven environment to steer timely project completion and within budgetary constraints.}
\sectionsep
\sectionsep

% %%%%%%%%%%%%%%%%%%%% comment these lines out after reading it 
% \hl{hey Max, this is a good start. Download this template as well for the longer CV version

% https://www.overleaf.com/latex/templates/software-engineer-resume/gqxmqsvsbdjf. 

% Just download the files and upload them to the folder longer version}

% For this particular CV, 

% \textbf{>>>>>}For the title, add relevant links. Since your website is a bit broken, its negative PR, don't add it now. First fix it. Add links that help your case (github, stackoverflow, linkedin? etc). Add one number and one email for address. I would advise you to build a small portfolio site with github.io that's a bit more sustainable and less likely to be hacked/compromised. Look at this website (\url{https://jacekjeznach.com/about}) when you see it you definitely know the guy is on point and he know his stuff. Build a website that supports the narrative you want to portray.

% \textbf{>>>>}For the columns,  introduction of yourself should be on the top left (I am interested in web development and have worked with Ajax, etc... Something that summarizes the CV somewhat) -- no need to title that one, (e.g \url{https://novoresume.com/career-blog/software-engineer-resume})
% On the top right, title (Education --- Add University and High-school. Don't add uni grades it might negatively sway someone since it's not first class) 
% Second thing on left should be Work Experience. Mention the company and time you worked and small details or project highlights on the that job. 
% On the right hand side below Education, add Awards. Mention any awards or honors you've received. 
% On the left after Work Experience, Mention projects. One sentence description of what the project is about. If there is a link, Github or otherwise, add it. 
% On the right after awards and honors, add Skills. 
% On the left after Projects if there is space, add Service,. Here add the volunteering experiences you've been part of and what volunteering you did. 
% On the right after Skills, add  miscellaneous. Under miscellaneous add any certifications you've earned and relevant organizations you're part of.
% Lastly, across from left to right, add references. Start with Maximumus, the Yuichi and lastly Charled on the same row left to right.

% \hl{you tend to use capital letters for your name and in emails. Using caps is interpreted as shouting. It's better to you First letter only caps for the name. }

% %%%%%%%%%%%%%%%%%%%% comment these lines out after reading it 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Computer Medics Limited}
\descript{|Software Developer}
\location{May 2022 – Up-to-date | Rumee Towers, Nakasero, Kampala}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Currently employed as full time Senior Back-end software developer in Python for different projects. 
\item Also part of the DevOps team for different several projects.
\end{tightemize}

\sectionsep
\sectionsep

\runsubsection{Shopto Uganda Limited}
\descript{|Senior Back-end Engineer}
\location{April 2019 – June 2021 | Kampala, Uganda}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Started as a Junior back-end developer in Ruby and Ruby on rails.
\item Later Promoted to Senior back-end developer in Python and Django. \item Among the roles was developing a USSD application to use on phones that are not smartphones
\end{tightemize}

\sectionsep
\sectionsep

\runsubsection{Makerere University - ARMS Project}
\descript{| Software Developer }
\location{May 2016 – March 2018 | Makerere University, Kampala.}

\begin{tightemize}
\item Designed and implemented a Digital signage System at the college of engineering, Design, Art and technology that helps in information dissemination on the screens in the college, using Raspberry Pi technologies.
\item Designed and implemented an MVP of an election/poll system to aid in student leadership elections at the same college.
\item Website design and development.
\end{tightemize}
\sectionsep
\sectionsep

\runsubsection{Retirement Life Hub}
\descript{C.T.O | Web Developer }
\location{September 2019 – January 2022 | Kyanja, Kampala}

\begin{tightemize}
\item Chief Technology Officer – Always work hand in hand with the CEO in brainstorming and implementing strategies for the development of the company's Technology for better service delivery.
\item Bulk email and social media management
\end{tightemize}

\sectionsep
\sectionsep

\runsubsection{ Free Lance Software Developer }
\descript{| Python, Ruby, JavaScript }
\location{Since 2016 | Kampala}

\begin{tightemize}
\item Since 2016, I have been working on freelance projects and solutions with different teams and companies, the latest being an auto irrigation and garden environment monitoring system
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}\label{sec:projects}

\runsubsection{Judicial Service Commission Human Resource System}
\descript{| Python / Django / React}
\location{2022}

\begin{tightemize}
\item Developing the Back-end of the Human resource of the Judicial council of Uganda known as the Judicial Service commission
\item Managing Databases, Hosting, and maintenance of the servers on which the system is hosted.
\item DevOps lead on the entire project
\end{tightemize}
\sectionsep

\runsubsection{Irrigation App}
\descript{| Python / Django}
\location{2021}
\begin{tightemize}
\item This app helps monitor soil conditions like temperature and moisture and alerts users in case there is need to irrigate or add fertilizers.
\item It incorporates AI that predicts chances of raining depending on \\ the environmental conditions
\end{tightemize}
\sectionsep

\runsubsection{Shopto Apps}
\descript{| Ruby/ Ruby on Rails and Python/Django}
\location{2019-2021}
\begin{tightemize}
\item Shopto App is an Inventory management system for shops. 
\item Shopto delivery App is a system for making orders, purchase delivery for shop items especially to remote shops.
\end{tightemize}
\sectionsep

\runsubsection{Farmgain App}
\descript{|  Python/Django}
\location{2020}
\begin{tightemize}
\item This is a system for connecting farmers to buyers in big markets all around Uganda  
\item It eliminates the middle man effect of under pricing farmers.
\end{tightemize}
\sectionsep

\runsubsection{Design Projects}
\descript{|  Adobe Illustrator | Figma | Adobe XD | Adobe Photoshop}
\location{SInce 2016}
\begin{tightemize}
 \item Worked on several designs for web, print and branding in the above software
 \item Built UIs for different Mobile Apps and Web Apps
\end{tightemize}
\sectionsep

\runsubsection{Various Websites}
\descript{| WordPress | Python | HTML and JavaScript}
\begin{tightemize}
\item I have designed, developed and maintained various number of websites that are still active and fully functional with total customer satisfaction.
\end{tightemize}
\sectionsep

\section{Service | Voluntary Work}
\begin{tightemize}
\item I trained young innovators at an innovation camp in Soroti, sponsored by MIT-DLab when I was reached out to by Resilient Africa Network (RAN) in January 2019.
\item I also volunteered to teach students from different schools on how to integrate technology with Agriculture at UCU Mukono, sponsored by RAN
\item As an Africa code week implementing partner, I have since 2017 been volunteering to teach coding and problem-solving skills using technology to students from as young as 9. The project is sponsored by SAP, Irish Embassy, UNESCO and many more.
\item I carried out a training to local farmers in Northern Uganda and the West-Nile, developed a system for them to help them catalogue their produce with the prices using smartphones. This has helped them eliminate the problem of middle-men unfair pricing of their produce. This project was sponsored by Action for Livelihood Enhancement in Northern Uganda (ALENU), Office of the prime minister, DINU,CARITAS, AFARD, GWED-G and European Union in October 2020.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \end{minipage} 
\hfill
% \begin{minipage}[t]{0.29\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Skills}

\begin{multicols}{3}

\subsection{Programming}
Python \textbullet{} Ruby \textbullet{} JavaScript

Android Development \\ Kotlin \textbullet{} Flutter
\columnbreak

\subsection{Libraries/Frameworks}
{Node.js \textbullet{} Django \textbullet{}  React \textbullet{} MySQL \textbullet{} Postgres }

\columnbreak

\subsection{Tools/Platforms}
A.W.S \textbullet{} Github \textbullet{} Docker \textbullet{} Heroku \textbullet{} GCP \textbullet{} Wordpress
\end{multicols}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}\label{sec:education}
\begin{multicols}{3}
\subsection{Makerere University}\label{subsec:makerere-university}
\descript{Bachelor's in Computer Engineering}
\location{Sep 2015 - Jan 2020 | Kampala, Uganda}
College of Engineering, Design, Art and Technology \\
\sectionsep
\sectionsep
\columnbreak

\subsection{Ntungamo High School}\label{subsec:ntungamo-high-school}
\descript{Uganda Advanced Certificate of Education}
\location{March 2013 - Dec 2014 | Ntungamo, Uganda}
\sectionsep
\sectionsep
\columnbreak

\subsection{Bishop Ogez High School}\label{subsec:bishop-ogez-high-school}
\descript{ Uganda  Certificate of Education}
\location{Feb 2009 - Nov 2012 | Bushenyi, Uganda}
\sectionsep
\end{multicols}

\sectionsep
\sectionsep
\section{Awards / Honors}\label{sec:awards-/-honors}
\begin{multicols}{3}
\subsection{CodeIT Institute of Technology}\label{subsec:codeit-institute-of-technology}
\descript{Certificate in Python, BlockChain and AWS}
\location{Jan 2021 | The Innovation Village Kampala}
\sectionsep
\sectionsep
\columnbreak

\subsection{Africa code Week}\label{subsec:africa-code-week}
\descript{Certificate for Training (others) programming Using Scratch}
\location{Annually since 2017 }
\sectionsep
\sectionsep
\columnbreak

\subsection{MIT  | D-lab}\label{subsec:mit--|-d-lab}
\descript{Certificate of collaboration to finding practical solutions to alleviate poverty}
\location{January 2019}
\sectionsep
\end{multicols}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     REFERENCES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{References}\label{sec:references}
\begin{multicols}{3}
\color{BlueGreen}
\sectionsep
{\textbf{Mr. Makumbi Richard }}, \\ C.E.O, Computer Medics Limited \\
 \faEnvelope \quad makumbi@cml.ug \\ \faPhone \quad +256772377777
\sectionsep
\columnbreak

{\textbf{Mr. Kennedy Nayebare}, \\ Project Manager, Computer Medics Limited} \\
 \faEnvelope \quad knayebare@gmail.com \\ \faPhone \quad  +256779218440
\sectionsep
\columnbreak

{\textbf{Dr. Charles Barugahare }}, \\ Former, University Secretary, Makerere \\
 \faEnvelope \quad cbaruga1@gmail.com \\ \faPhone  \quad+256772457466 
\end{multicols}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Graduate}
% Graduate Algorithms \textbullet{}\\ 
% Advanced Computer Architecture \textbullet{}\\ 
% Operating Systems \textbullet{}\\ 
% Artificial Intelligence \textbullet{}\\
% Visualization For Scientific Data \\
% \sectionsep

% \subsection{Undergraduate}

% Database Management Systems \textbullet{}\\
% Object Oriented Analysis and Design \textbullet{}\\
% Artificial Intelligence and Expert Systems \textbullet{}\\
% Scripting Languages and Web Tech \textbullet{}\\
% Software Engineering \\

% \end{minipage} 
\end{document}  \documentclass[]{article.cls}

